---
title       : Iris Measurement Data - Shiny App Guide
subtitle    : Developing Data Products (Coursera)
author      : darobertson
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---.class #id

## Introduction

The purpose of this shiny application is to calculate and display regression analysis regarding iris characteristics. The analysis is based on the following information selected by the user via drop-down boxes
 - Species
 - X Variable (Measurement)
 - Y Variable (Measurement)


--- .class #id

## UI.R code

```{r}
library(shiny)

# Define UI for dataset viewer application
shinyUI(pageWithSidebar(
  
  # Application title
  headerPanel("Iris Measurements"),
  
  # Sidebar with controls
  sidebarPanel(
    selectInput("species", "Choose a Species:", 
                choices = c("setosa", "versicolor", "virginica")),
    selectInput('xcol', 'X Variable', names(iris[,1:4])),
    selectInput('ycol', 'Y Variable', names(iris[,1:4]),
                selected=names(iris)[[2]])
  ),    

  # Plot the quantitative data selected for that species
mainPanel(
      
      verbatimTextOutput("summary"),
      
      plotOutput("plot1")
    )
  ))
```

---.class #id

## Server.R code 
### Summarizes and plots the selected iris data

```{r}
library(shiny)
library(datasets)
data(iris)

# Define server logic required to summarize and view the selected dataset
shinyServer(function(input, output) {

  # Combine the selected variables into a new data frame
   IrisDataset <- reactive({
    switch(input$species,
           "Setosa" = iris[iris$Species == "setosa",],
           "Versicolor" = iris[iris$Species == "versicolor",],
           "Virginica" = iris[iris$Species == "virginica",]
   selectedVariables <- reactive({
    IrisDataset[, c(input$xcol, input$ycol)]
  })

  output$plot1 <- renderPlot({
    plot(selectedVariables, main = c("Iris Regression for Species ", input$species))
  })

})
```
---.class #id


## Usage Example




---